---
title: "Working on the Website"
description: |
  How to get this thing working!
author:
  - name: Matthew D. Buehler
    url: {}
date: 12-10-2020
output:
  distill::distill_article:
    self_contained: false
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Getting Started on a Distill Website


A few days ago I found a blog post talking about using Distill as a compiler for simple websites.
I am more comfortable with R and Rmarkdown than I am with using something like Jekyll, but there were still quite a few bumps in the road getting the site functional

Installation of Distill is simple enough 

```{r, include=TRUE, echo=TRUE}

install.packages("distill")
library(distill)

```

The tricky part to setting up a Github website was figuring out where files are being written to and read in from. 
Some sites recommended that you write output from Distill to a _site directory, however, for me Github would only read from either the base directory or from a docs/ directory. 

## The Next Part